### 2023-03-13 manuscript.tex
* manuscript.tex: Adjust wording.

The pair of examples above suggests that the power of nonlinear
phonology comes not from the representations, nor from the capability
of iterative application.  Instead, it comes from the ability to
encode the associations in the transformations, as explicified by the
computational models.  Iterative application, on the other hand,
concerns the computational nature of the rules.  As a computer
scientist may say, a transformation is \enquote{mapped} to a sequence
in a certain order, resulting in the apparently long-distance
transformation.

A point should be made that iterative application has little to do
with the organization of grammar.  An iteratively applied phonological
transformation is neither inherently associated with cyclicity nor
with ordering.  In fact, it is not necessarily iterative at all under
an alternative representation.  The only thing relevant is the
\textemph{process} the rule generates as embodied by the equivalent
transducer.

>>>>

The pair of examples above suggests that the power of nonlinear
phonology comes not from the representations, nor from the capability
of iterative application.  Instead, it comes from the ability to
encode the associations in the transformations, as explicified by the
computational models.  Iterative application, on the other hand,
concerns the computational nature of the rules, which is reflected by
the mappings their corresponding process produces.

A point should be made that iterative application has little to do
with the organization of grammar.  An iteratively applied phonological
transformation is neither inherently associated with cyclicity nor
with ordering.  In fact, it is not necessarily iterative at all under
an alternative representation.  The only thing relevant is the
\textemph{process} the rule generates as embodied by the equivalent
computational device.
